RNeXML: a package for reading and writing richly annotated phylogenetic, character, and trait data in R

### 2015-01-08 manuscripts/manuscript.Rmd

      3. RNeXML can read any NeXML document that validates, and it
      generates valid NeXML documentes from phylogeny and character
      data from various R representations in use. The metadata
      programming interface at a basic level aids fulfilling data
      documentation best practices, and at an advanced level preserves
      NeXML's nearly limitless extensibility, for which we provide a
      fully working demonstration. Furthermore, to lower the barriers
      to sharing well-documented phylogenetic data, RNeXML has started
      to integrate with taxonomic metadata augmentation services on
      the web, and with online repositories for data archiving.

>>>>

      3. RNeXML can read any NeXML document that validates, and it
      generates valid NeXML documents from phylogeny and character
      data in various R representations in use. The metadata
      programming interface at a basic level aids fulfilling data
      documentation best practices, and at an advanced level preserves
      NeXML's nearly limitless extensibility, for which we provide a
      fully working demonstration. Furthermore, to lower the barriers
      to sharing well-documented phylogenetic data, RNeXML has started
      to integrate with taxonomic metadata augmentation services on
      the web, and with online repositories for data archiving.
